The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-14 code/eda-code/eda_MADAprojectcode.qmd
P Update

# Data Import & Initial Inspection 
```{r}
# Read the dataset
PROMO_Data <- read_csv(here("data", "raw-data", "PROMO_Data.csv"))

# **Dataset Overview**
cat("Number of Observations:", nrow(PROMO_Data), "\n")
cat("Number of Variables:", ncol(PROMO_Data), "\n")

# **Inspect Data Structure**
str(PROMO_Data)
head(PROMO_Data)

# **Check Missing Values**
missing_values <- colSums(is.na(PROMO_Data))
print(missing_values)

# **Summary Statistics**
summary(PROMO_Data)

@@

# Data Cleaning & Transformation
```{r}
# Clean Column Names**
PROMO_Data <- PROMO_Data %>% clean_names()

# **Remove Empty Rows**
PROMO_Data <- PROMO_Data %>%
  filter(!is.na(study_arm), !is.na(stillbirth), !is.na(neonatal_death), !is.na(infant_low_birth_weight_2500_g))

# **Handle Missing Values**
PROMO_Data <- PROMO_Data %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), median(., na.rm = TRUE), .))) %>%
  mutate(across(where(is.character), ~ replace_na(., "Unknown")))

# **Convert Data Types**
PROMO_Data <- PROMO_Data %>%
  mutate(across(c(study_arm, stillbirth, neonatal_death, placental_malaria, delivery_mode), as.factor)) %>%
  mutate(across(contains("date"), as.Date, format="%Y-%m-%d"))

# **Verify Changes**
str(PROMO_Data)

@@

# Exploratory Data Analysis (EDA)

```{r}
# **Summary of Numeric Variables**
skim(PROMO_Data)

# **Frequency Counts of Key Categorical Variables**
PROMO_Data %>%
  count(study_arm, sort = TRUE)

PROMO_Data %>%
  count(placental_malaria, sort = TRUE)

PROMO_Data %>%
  count(preterm_birth_ontoneo, sort = TRUE)

@@

# Characteristics Tables
*Baseline Characteristics Table*

```{r}
# Select key variables for baseline characteristics
baseline_vars <- c("study_arm", "education_level_omrse", "gravidity", "parity", 
                   "placental_malaria", "preterm_birth_ontoneo", "stillbirth", 
                   "neonatal_death", "infant_low_birth_weight_2500_g")

# **Ensure selected variables exist**
baseline_vars <- baseline_vars[baseline_vars %in% colnames(PROMO_Data)]

# Generate formatted table using gtsummary
baseline_characteristics <- PROMO_Data %>%
  select(all_of(baseline_vars)) %>%
  tbl_summary(by = study_arm) %>%
  add_p() %>%
  modify_header(label = "**Variable**") %>%
  bold_labels()

baseline_characteristics

@@

*Continuous Characteristics by Study Arm*

```{r}
# Function to summarize continuous variables
summarize_continuous <- function(var) {
  sp_mean <- mean(PROMO_Data[[var]][PROMO_Data$study_arm == "Sulphadoxine-pyrimethamine (SP)"], na.rm = TRUE)
  sp_sd <- sd(PROMO_Data[[var]][PROMO_Data$study_arm == "Sulphadoxine-pyrimethamine (SP)"], na.rm = TRUE)

  dp_mean <- mean(PROMO_Data[[var]][PROMO_Data$study_arm == "Dihydroartemisinin-piperaquine (DP)"], na.rm = TRUE)
  dp_sd <- sd(PROMO_Data[[var]][PROMO_Data$study_arm == "Dihydroartemisinin-piperaquine (DP)"], na.rm = TRUE)

  p_value <- t.test(PROMO_Data[[var]] ~ PROMO_Data$study_arm, var.equal = TRUE, na.rm = TRUE)$p.value

  return(c(sprintf("%.1f (%.1f)", sp_mean, sp_sd),
           sprintf("%.1f (%.1f)", dp_mean, dp_sd),
           sprintf("%.3f", p_value)))
}

# Create summary table
summary_table <- tibble(
  Characteristic = c("Maternal Age (years)", "Gravidity", "Gestational Age at Delivery (weeks)", "Malaria Episodes During Pregnancy"),
  `SP (Mean ± SD)` = sapply(c("age_at_enrollment_years", "gravidity", "gestational_age_at_delivery_weeks", "total_malaria_episodes_during_pregnancy"), summarize_continuous)[1,],
  `DP (Mean ± SD)` = sapply(c("age_at_enrollment_years", "gravidity", "gestational_age_at_delivery_weeks", "total_malaria_episodes_during_pregnancy"), summarize_continuous)[2,],
  `p-value` = sapply(c("age_at_enrollment_years", "gravidity", "gestational_age_at_delivery_weeks", "total_malaria_episodes_during_pregnancy"), summarize_continuous)[3,]
)

# Display table using gt
summary_table %>%
  gt() %>%
  tab_header(title = md("**Table: Continuous Characteristics by Study Arm**")) %>%
  cols_align(align = "center") %>%
  tab_options(
    table.font.size = px(12),
    heading.title.font.size = px(14),
    table.border.top.style = "solid",
    table.border.bottom.style = "solid"
  )

@@

```{r}
colnames(PROMO_Data)

@@

```{r}
# Load required libraries
# Load required libraries
library(dplyr)
library(gtsummary)

# Define malaria outcome variables
malaria_outcome_vars <- c(
  "total_malaria_episodes_during_pregnancy",
  "placental_malaria",
  "preterm_birth_ontoneo",
  "stillbirth",
  "infant_low_birth_weight_2500_g"
)

# Ensure that `study_arm` is in the dataset
if (!"study_arm" %in% colnames(PROMO_Data)) {
  stop("⚠️ Error: `study_arm` column not found in PROMO_Data. Please check column names.")
}

# Remove `stillbirth` and any other variable that has only one level
valid_outcomes <- malaria_outcome_vars[sapply(PROMO_Data[malaria_outcome_vars], function(x) length(unique(na.omit(x))) > 1)]

# Ensure `study_arm` is included in the selected variables
valid_outcomes <- c(valid_outcomes, "study_arm")

# Define label mappings dynamically based on valid variables
all_labels <- list(
  total_malaria_episodes_during_pregnancy ~ "Total Malaria Episodes (Mean ± SD)",
  placental_malaria ~ "Placental Malaria (Histology)",
  preterm_birth_ontoneo ~ "Preterm Birth",
  stillbirth ~ "Stillbirth",
  infant_low_birth_weight_2500_g ~ "Low Birth Weight (<2500g)"
)

dynamic_labels <- all_labels[names(all_labels) %in% valid_outcomes]

# Define a custom function to format p-values
format_pvalue <- function(pvals) {
  sapply(pvals, function(x) {
    if (is.na(x)) {
      return("NA")  # Handle missing values properly
    } else if (is.numeric(x)) {
      if (x < 0.001) {
        return("< 0.001")  # Report very small values as "< 0.001"
      } else if (x < 0.01) {
        return(format(round(x, 3), nsmall = 3))  # Report between 0.001 and 0.01 to three decimal places
      } else {
        return(format(round(x, 2), nsmall = 2))  # Report >= 0.01 to two decimal places
      }
    } else {
      return("NA")  # Return "NA" for non-numeric values
    }
  })
}

# Generate table with formatted p-values
if (nrow(PROMO_Data) > 0 && length(valid_outcomes) > 1) {

  malaria_outcomes_table <- PROMO_Data %>%
    select(all_of(valid_outcomes)) %>%
    tbl_summary(
      by = "study_arm",
      statistic = list(
        total_malaria_episodes_during_pregnancy ~ "{mean} ± {sd}",
        all_categorical() ~ "{n} ({p}%)"
      ),
      label = dynamic_labels
    ) %>%
    add_p(
      test = list(
        all_categorical() ~ "fisher.test",
        all_continuous() ~ "t.test"
      ),
      pvalue_fun = format_pvalue  # Apply the fixed p-value formatting function
    )

  # Print the updated table
  print(malaria_outcomes_table)

} else {
  message("⚠️ No data available for analysis or insufficient variability in variables.")
}
```

>>>>

# Data Import & Initial Inspection 
```{r}
# Data Import & Initial Inspection 
# load the Dataset
PROMO_Data <- read_csv(here("data", "raw-data", "PROMO_Data.csv"))

@@

# Data Cleaning & Transformation
```{r}
#  Clean Column Names
PROMO_Data <- PROMO_Data %>%
  clean_names()  # Standardizes column names (lowercase, removes spaces/special characters)

#   Check for Missing Values
missing_summary <- colSums(is.na(PROMO_Data))
print("Missing Values Summary:")
print(missing_summary)

#  Handle Missing Values
PROMO_Data <- PROMO_Data %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), median(., na.rm = TRUE), .))) %>%  # Replace NA in numeric columns with median
  mutate(across(where(is.character), ~ replace_na(., "Unknown")))  # Replace NA in categorical columns with "Unknown"

#   Convert Data Types
PROMO_Data <- PROMO_Data %>%
  mutate(across(c(study_arm, delivery_mode, education_level), as.factor)) %>% # Convert categorical columns to factors
  mutate(across(contains("date"), as.Date, format="%Y-%m-%d"))  # Convert date columns

#  Rename Key Variables for Clarity
PROMO_Data <- PROMO_Data %>%
  rename(
    `Study Arm` = study_arm,
    `Gestational Age at Enrollment (Weeks)` = gestational_age_at_enrollment_weeks,
    `Gestational Age at Delivery (Weeks)` = gestational_age_at_delivery,
    `Education Level` = education_level,
    `Detection of Malaria Parasites by Microscopy` = proportion_of_plasmodium_positive_blood_smears_during_pregnancy_by_microscopy,
    `Detection of Malaria Parasites by Microscopy or qPCR` = total_plasmodium_positive_routine_blood_smears_during_pregnancy
  )

#   Remove Duplicate Rows
PROMO_Data_Cleaned <- PROMO_Data %>%
  distinct()  # Removes exact duplicate rows

#  Step 7: Print Summary of Cleaned Data
summary(PROMO_Data_Cleaned)

#   Display Column Names to Verify
print("Updated Column Names:")
print(colnames(PROMO_Data_Cleaned))

@@

```{r}
colnames(PROMO_Data_Cleaned)

@@

# Exploratory Data Analysis (EDA)
```{r}
# Number of observations and variables
cat("Number of Observations:", nrow(PROMO_Data_Cleaned), "\n")
cat("Number of Variables:", ncol(PROMO_Data_Cleaned), "\n")

# View structure of dataset
str(PROMO_Data_Cleaned)

# Quick Summary Statistics
summary(PROMO_Data_Cleaned)

@@

*Step 1: Fix Missing Data & Categorize Variables*
*Baseline Characteristics Table 1*
```{r}
library(dplyr)
library(gtsummary)

# ✅ Fix & Categorize Variables
PROMO_Data_Cleaned <- PROMO_Data_Cleaned %>%
  mutate(
    Age_Category = case_when(
      age_at_enrollment_years < 18 ~ "<18 (Minors)",
      age_at_enrollment_years >= 18 & age_at_enrollment_years <= 35 ~ "18–35 (Young Adults)",
      age_at_enrollment_years >= 36 & age_at_enrollment_years <= 55 ~ "36–55 (Middle-aged)",
      age_at_enrollment_years > 55 ~ ">55 (Older Adults)",
      TRUE ~ "Unknown"
    ),

    # ✅ Fix Education Level Categorization (Put "Unknown" Last)
    `Education Level` = case_when(
      `Education Level` %in% c("A level", "O level", "None") ~ "Secondary/No Formal Education",
      `Education Level` == "Primary" ~ "Primary",
      `Education Level` %in% c("Tertiary", "University") ~ "Tertiary/Higher Education",
      is.na(`Education Level`) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("Primary", "Secondary/No Formal Education", "Tertiary/Higher Education", "Unknown")),

    # ✅ Fix Gravidity Categorization (Put "Unknown" Last)
    Gravidity = case_when(
      gravidity == 1 ~ "1",
      gravidity == 2 ~ "2",
      gravidity >= 3 ~ "≥3",
      is.na(gravidity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown")),

    # ✅ Fix Parity Categorization (Put "Unknown" Last)
    Parity = case_when(
      parity == 1 ~ "1",
      parity == 2 ~ "2",
      parity >= 3 ~ "≥3",
      is.na(parity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown"))
  )
# ✅ Define Variables (Maternal Info First, Infant Last)
baseline_vars <- c(
  # **Maternal Information**
  "Age_Category", 
  "Education Level",
  "Gravidity", 
  "Parity", 
  "Gestational Age at Enrollment (Weeks)", 
  "Gestational Age at Delivery (Weeks)", 
  "placental_malaria", 
  "total_malaria_episodes_during_pregnancy", 
  "delivery_mode",

  # **Pregnancy Outcomes**
  "preterm_birth", 
  "small_for_gestational_age", 
  "spontaneous_abortion", 
  "stillbirth", 
  "neonatal_death",

  # **Infant Information**
  "infant_low_birth_weight_2500_g", 
  "infant_sex6"
)

# ✅ Ensure Variables Exist in the Dataset
baseline_vars <- baseline_vars[baseline_vars %in% colnames(PROMO_Data_Cleaned)]

# ✅ Create Updated Table (Remove Label Name)
baseline_table <- PROMO_Data_Cleaned %>%
  select(all_of(baseline_vars), `Study Arm`) %>%
  tbl_summary(
    by = `Study Arm`,
    statistic = all_categorical() ~ "{n} ({p}%)",
    missing = "no"
  ) %>%
  modify_header(label = "") %>% # Remove the label name
  bold_labels()

# ✅ Display Table
baseline_table
```

```{r}
PROMO_Data_Cleaned <- PROMO_Data_Cleaned %>%
  mutate(
    Age_Category = case_when(
      age_at_enrollment_years < 18 ~ "<18 (Minors)",
      age_at_enrollment_years >= 18 & age_at_enrollment_years <= 35 ~ "18–35 (Young Adults)",
      age_at_enrollment_years >= 36 & age_at_enrollment_years <= 55 ~ "36–55 (Middle-aged)",
      age_at_enrollment_years > 55 ~ ">55 (Older Adults)",
      TRUE ~ "Unknown"
    ),

    # ✅ Fix Education Level Categorization (Include "Unknown")
    `Education Level` = case_when(
      `Education Level` %in% c("A level", "O level", "None") ~ "Secondary/No Formal Education",
      `Education Level` == "Primary" ~ "Primary",
      `Education Level` %in% c("Tertiary", "University") ~ "Tertiary/Higher Education",
      is.na(`Education Level`) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("Primary", "Secondary/No Formal Education", "Tertiary/Higher Education", "Unknown")),

    # ✅ Fix Gravidity Categorization (Include "Unknown")
    gravidity = case_when(
      gravidity == 1 ~ "1",
      gravidity == 2 ~ "2",
      gravidity >= 3 ~ "≥3",
      is.na(gravidity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown")),

    # ✅ Fix Parity Categorization (Include "Unknown")
    parity = case_when(
      parity == 1 ~ "1",
      parity == 2 ~ "2",
      parity >= 3 ~ "≥3",
      is.na(parity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown"))
  )

PROMO_Data_Cleaned <- PROMO_Data_Cleaned %>%
  mutate(
    Age_Category = case_when(
      age_at_enrollment_years < 18 ~ "<18 (Minors)",
      age_at_enrollment_years >= 18 & age_at_enrollment_years <= 35 ~ "18–35 (Young Adults)",
      age_at_enrollment_years >= 36 & age_at_enrollment_years <= 55 ~ "36–55 (Middle-aged)",
      age_at_enrollment_years > 55 ~ ">55 (Older Adults)",
      TRUE ~ "Unknown"
    ),

    # ✅ Fix Education Level Categorization (Include "Unknown")
    `Education Level` = case_when(
      `Education Level` %in% c("A level", "O level", "None") ~ "Secondary/No Formal Education",
      `Education Level` == "Primary" ~ "Primary",
      `Education Level` %in% c("Tertiary", "University") ~ "Tertiary/Higher Education",
      is.na(`Education Level`) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("Primary", "Secondary/No Formal Education", "Tertiary/Higher Education", "Unknown")),

    # ✅ Fix Gravidity Categorization (Include "Unknown")
    gravidity = case_when(
      gravidity == 1 ~ "1",
      gravidity == 2 ~ "2",
      gravidity >= 3 ~ "≥3",
      is.na(gravidity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown")),

    # ✅ Fix Parity Categorization (Include "Unknown")
    parity = case_when(
      parity == 1 ~ "1",
      parity == 2 ~ "2",
      parity >= 3 ~ "≥3",
      is.na(parity) ~ "Unknown",
      TRUE ~ "Unknown"
    ) %>% factor(levels = c("1", "2", "≥3", "Unknown"))
  )

# ✅ Define Baseline Characteristics Variables
baseline_vars <- c(
  # **Maternal Information First**
  "Age_Category", 
  "Education Level",
  "Gravidity", 
  "Parity", 
  "Gestational Age at Enrollment (Weeks)", 
  "Gestational Age at Delivery (Weeks)", 
  "placental_malaria", 
  "total_malaria_episodes_during_pregnancy", 
  "delivery_mode",

  # **Pregnancy Outcomes**
  "preterm_birth", 
  "small_for_gestational_age", 
  "spontaneous_abortion", 
  "stillbirth", 
  "neonatal_death",

  # **Infant Information**
  "infant_low_birth_weight_2500_g", 
  "infant_sex6"
)

# ✅ Ensure Variables Exist in the Dataset
baseline_vars <- baseline_vars[baseline_vars %in% colnames(PROMO_Data_Cleaned)]

# ✅ Create Updated Baseline Characteristics Table
baseline_table <- PROMO_Data_Cleaned %>%
  select(all_of(baseline_vars), `Study Arm`) %>%
  tbl_summary(
    by = `Study Arm`,
    statistic = all_categorical() ~ "{n} ({p}%)",
    missing = "no"
  ) %>%
  modify_header(label = "**Baseline Characteristics**") %>%
  bold_labels()

# ✅ Display the Table
baseline_table

@@

```{r}
# Load required packages
library(dplyr)
library(gtsummary)

# ✅ Step 1: Categorize Age into Clinically Meaningful Groups
PROMO_Data_Cleaned <- PROMO_Data_Cleaned %>%
  mutate(
    # ✅ Age Category
    Age_Category = case_when(
      age_at_enrollment_years < 18 ~ "<18 (Minors)",
      age_at_enrollment_years >= 18 & age_at_enrollment_years <= 35 ~ "18–35 (Young Adults)",
      age_at_enrollment_years >= 36 & age_at_enrollment_years <= 55 ~ "36–55 (Middle-aged)",
      age_at_enrollment_years > 55 ~ ">55 (Older Adults)",
      TRUE ~ NA_character_
    ),

    # ✅ Fix Education Level Categorization (Ensuring it’s Correct)
    Education_Level = case_when(
      `Education Level` %in% c("A level", "O level", "None") ~ "Secondary/No Formal Education",
      `Education Level` %in% c("Primary") ~ "Primary",
      `Education Level` %in% c("Tertiary", "University") ~ "Tertiary/Higher Education",
      TRUE ~ NA_character_
    ),

    # Convert to Factor with Proper Levels
    Education_Level = factor(Education_Level, levels = c("Primary", "Secondary/No Formal Education", "Tertiary/Higher Education")),

    # ✅ Categorize Gravidity
    Gravidity = factor(case_when(
      gravidity == 1 ~ "1",
      gravidity == 2 ~ "2",
      gravidity >= 3 ~ "≥3",
      TRUE ~ NA_character_
    ), levels = c("1", "2", "≥3")),

    # ✅ Categorize Parity
    Parity = factor(case_when(
      parity == 1 ~ "1",
      parity == 2 ~ "2",
      parity >= 3 ~ "≥3",
      TRUE ~ NA_character_
    ), levels = c("1", "2", "≥3"))
  )

# ✅ Step 2: Define the 16 Key Variables for the Table
baseline_vars <- c(
  # 🟢 **Mother's Demographics & Reproductive History**
  "Age_Category", 
  "Education_Level",  # ✅ Fixed Education Level Here
  "Gravidity",
  "Parity",
  "Gestational Age at Enrollment (Weeks)", 
  "Gestational Age at Delivery (Weeks)", 
  "Placental_malaria", 
  "Total_malaria_episodes_during_pregnancy",
  "Study Arm",  # Treatment assignment (SP vs DP)
  "Delivery_mode",

  # 🟡 **Pregnancy & Birth Outcomes**
  "Preterm_birth", 
  "Small_for_gestational_age", 
  "Spontaneous_abortion", 
  "Stillbirth", 
  "Neonatal_death",

  # 🔵 **Infant Birth Outcomes**
  "Infant_low_birth_weight_2500_g", 
  "Infant_sex6"
)

# ✅ Step 3: Ensure Variables Exist in the Dataset
baseline_vars <- baseline_vars[baseline_vars %in% colnames(PROMO_Data_Cleaned)]

# ✅ Step 4: Confirm Total Variables
cat("Total Variables Selected:", length(baseline_vars), "\n")  # Should output 16

# ✅ Step 5: Create the Baseline Characteristics Table
baseline_table <- PROMO_Data_Cleaned %>%
  select(all_of(baseline_vars), `Study Arm`) %>%
  tbl_summary(
    by = `Study Arm`,
    statistic = all_categorical() ~ "{n} ({p}%)",
    missing = "no"
  ) %>%
  modify_header(label = "**Baseline Characteristics**") %>%
  bold_labels()

# ✅ Step 6: Display the Table
baseline_table

@@

*Figure 1: Pregnancy Outcomes by Study Arm*
```{r}
# Load required packages
library(ggplot2)
library(dplyr)
library(tidyr)

# Ensure correct column name for Study Arm
study_arm_col <- "Study Arm"

# Define pregnancy outcomes
pregnancy_outcomes <- c("preterm_birth", "stillbirth", "neonatal_death")

# Reshape data for plotting
pregnancy_data <- PROMO_Data_Cleaned %>%
  select(all_of(study_arm_col), all_of(pregnancy_outcomes)) %>%
  pivot_longer(cols = all_of(pregnancy_outcomes), names_to = "Outcome", values_to = "Present") %>%
  filter(!is.na(Present)) %>%  # Remove missing values
  group_by(across(all_of(study_arm_col)), Outcome, Present) %>%
  summarise(Total = n(), .groups = "drop")

# Convert outcome values to categorical (if numeric)
pregnancy_data$Present <- factor(pregnancy_data$Present, levels = c(0, 1), labels = c("Absent", "Present"))

# Plot Pregnancy Outcomes by Study Arm
ggplot(pregnancy_data, aes(x = Outcome, y = Total, fill = !!sym(study_arm_col))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Pregnancy Outcomes by Study Arm",
       x = "Pregnancy Outcome",
       y = "Total Count",
       fill = "Study Arm") +
  theme_minimal() +
  scale_fill_manual(values = c("lightblue", "pink")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

*Placental Malaria by Study Arm*
```{r}
# Group and summarize data for placental malaria
# Ensure correct column name for Study Arm
study_arm_col <- "Study Arm"

# Group and summarize data for placental malaria
placental_malaria_data <- PROMO_Data_Cleaned %>%
  group_by(across(all_of(study_arm_col)), placental_malaria) %>%
  summarise(Count = n(), .groups = "drop")

# Convert placental malaria values to categorical (if numeric)
placental_malaria_data$placental_malaria <- factor(placental_malaria_data$placental_malaria, 
                                                   levels = c(0, 1), 
                                                   labels = c("No", "Yes"))

# Plot Placental Malaria by Study Arm
ggplot(placental_malaria_data, aes(x = placental_malaria, y = Count, fill = !!sym(study_arm_col))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Placental Malaria by Study Arm",
       x = "Placental Malaria",
       y = "Total Count",
       fill = "Study Arm") +
  theme_minimal() +
  scale_fill_manual(values = c("lightblue", "lightgreen")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r}
# Load required libraries
library(dplyr)
library(gtsummary)
